A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-09-03 ionic_liquids.tex
Some changes in the beginning of Sec 2

In this section, we present the formalism that allows us to compute the Henry constant and activity coefficient, both at infinite dilution, from the simulated free energy.
For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}.
Then, we reformulate the equations in order to study concentrated solutions, which would be the more likely scenario in \ce{CO_2} capture processes.

\subsection*{Solvation free energy}
The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from the gas phase to the solution.
For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to connect the ``endpoint'' states, whose free energy difference is to be estimated.
In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_\text{\tiny IL}$,P,T) and ($N_s^l$,$N_\text{\tiny IL}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.

>>>>

In this section, we present the formalism that allows us to compute solvation free energies from molecular dynamics simulations and, after that, obtain Henry constants and activity coefficients.
For dealing with systems at infinite dilution, we rely on the work of Shirts \textit{et al}. \cite{Shirts_2003}.
Then, we reformulate the equations in order to study concentrated solutions, which is a more likely scenario in the case of \ce{CO_2} capture processes.

\subsection*{Solvation free energy}

The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from a gas phase to the solution.
For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to reversibly connect the endpoint states whose difference in free energy is to be estimated.
In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the solute-solvent interactions by taking values in the interval [0,1]. By convention, $\lambda = 1$ corresponds to a fully interacting system, while for $\lambda$ = 0 the solute-solvent interactions are turned off completely .

In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_\text{\tiny IL}$,P,T) and ($N_s^l$,$N_\text{\tiny IL}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
